---
title: "Fourier Dojo"
output:
  html_notebook: default
  pdf_document: default
---

# Music

Load the tuneR library for the notebook.
```{r}
library(tuneR)
library(signal)
```

Read the Wave file into the wav object.
```{r}
wavFile <- '~/code/R/Fourier/LongSong.wav'
nuWavFile <- '~/code/R/Fourier/LongSongFiltered.wav'

cutoffFreq <- 2000
```

the readWave function reads wav files as integer types. Our wav file has a 16-bit depth `wav@bit`, this means that the sound pressure values are mapped to integer values that can range from -2^15 to (2^15)-1. We can convert our sound array to floating point values ranging from -1 to 1 as follows:
```{r}
wav <- readWave(wavFile)
s1 <- wav@left
s1 <- s1 / 2^(wav@bit - 1) # s1 -> floating point between -1 and 1.
s1.length <- length(s1)
```

```{r}
ts <- (0:(length(s1) - 1)) / wav@samp.rate * 1000
plot(ts, s1, type='l', xlab='Time (ms)', ylab='Amplitude')
```

Plot the signal between 50 and 100 milliseconds. (TODO: Correct for sample rate)
```{r}
plot(ts[2000:4000], s1[2000:4000], type='l', xlab='Time (ms)', ylab='Amplitude')
```

```{r}
s1.fft <- fft(s1)
f1.length <- length(s1.fft)
f1.unique <- ceiling((f1.length + 1)/2)
f1 <- s1.fft[0:f1.unique]
f1.scaled <- abs(f1) / s1.length
#f1.decibel <- f1 ^ 2
```

```{r}
fs <- (0:(f1.unique -1)) * (wav@samp.rate / s1.length)
```

Plot the frequency spectrum of wav:
```{r}
plot(fs, 1000*(f1.scaled), type='l', xlab='Frequency (mHz)', ylab='Amplitude')
```

```{r}
cutoffBnd <- ceiling((length(s1.fft)/2)*(cutoffFreq/(wav@samp.rate/2)))
```

Zoom in to the cutoff frequency spectrum of wav:
```{r}
plot(fs[1:cutoffBnd], (1000*(f1.scaled))[1:cutoffBnd], type='l', xlab='Frequency (mHz)', ylab='Amplitude')
```

Filter the first `cutoffBnd` data points in the spectrum (roughly `cutoffFreq` Hz) and plot:

```{r}
f1.filtered <- s1.fft
f1.filtered[cutoffBnd:(f1.length - 1)] <- 0
plot(1:ceiling(1.10 * cutoffBnd), abs(f1.filtered)[1:ceiling(1.10 * cutoffBnd)], type='l', xlab='Frequency (Hz)', ylab='Amplitude')
```

Apply the Inverse Fourier Transform to `f1.filter`.

```{r}
s2 <- ifft(f1.filtered)
```

```{r}
s2.scaled <- Re(round(s2 * 2^(wav@bit - 1)))
plot(0:(length(s2.scaled) - 1), s2.scaled, type='l', xlab='Time (ms)', ylab='Amplitude')
```
```{r}
plot(0:(length(s2.scaled) - 1), s2.scaled, type='l', xlab='Time (ms)', ylab='Amplitude')
```

```{r}
nuWav <- wav
nuWav@left <- s2.scaled
str(nuWav)
```

Write our filtered signal to a file. Declare victory.

```{r}
writeWave(nuWav, filename = nuWavFile)
```

# Images

```{r}
library(imager)
```

